SoK: Web Application Attack Defenses (in Question)

### 2014-10-12 docs/questioning.tex
defense categorisation

\maketitle
\begin{abstract}
In this paper we examine how application attack defense
mechanism are developed and presented to
the research community.
\end{abstract}

@@

@@

The basic problem behind web application attacks involves
the absence of input validation. By taking advantage of
this, attackers can inject their code into
applications to perform malicious tasks. Such
an exploit can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:taxonomy}Attack model demonstrating web
application attacks that involve code injection.}
\end{figure*}

@@

@@

\section{Covered Area}

We decided to narrow down our
research to countermeasures developed to
detect attacks that target applications. Such attacks include
buffer overflow attacks~\cite{K11}, {\sc sql} injection
attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
attacks~\cite{LZRL09} and others.
Such attacks top the vulnerability lists of numerous bulletin providers for several
years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
(Open Web Application Security Project)
Top Ten project whose main goal is to raise awareness about
web application security by identifying some of the most critical risks facing
organizations which is referenced by numerous researchers.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five positions.
This indicates that
apart from the fact that malicious users find new ways to bypass
defense mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

>>>>

\maketitle
\begin{abstract}
Web application attacks, can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.
Some of the most dangerous web application attacks,
like Cross-Site Scripting and {\sc sql} injection,
involve the exploitation of the following weakness:
programmers tend to develop applications that may
accept and process data of uncertain origin without
appropriate validation and / or filtering.
Such attacks have been constantly topping the lists
of the various security bulletin providers despite
the numerous countermeasures that have been proposed
over the past 15 years.

%In this paper we examine how application attack defense
%mechanism are developed and presented to
%the research community.
\end{abstract}

@@

% Notes
The attacks we examine include
{\sc sql} injection
attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
attacks~\cite{LZRL09} and others.
Such attacks top the vulnerability lists of numerous bulletin providers for several
years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
(Open Web Application Security Project)
Top Ten project whose main goal is to raise awareness about
web application security by identifying some of the most critical risks facing
organizations which is referenced by numerous researchers.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five positions.
This indicates that
apart from the fact that malicious users find new ways to bypass
defense mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

@@

The basic problem behind the most dangerous
web application attacks involves
the absence of input validation. By taking advantage of
this, attackers can inject their code into
applications to perform malicious tasks. Such
an exploit can have different forms depending on the
execution context of the application and the location
of the programming flaw that leads to the attack.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:taxonomy}Attack model demonstrating web
application attacks that involve code injection ({\sc draft}).}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{defenses.pdf}
\end{center}
\caption{\label{fig:taxonomy}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

@@
